Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia

### 2017-06-29 doc/manuscript/manuscript.Rmd
begin rewrite of methods

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amadarasa
    email: bamadarasa2@unl.edu
    affiliation: 1
  - name: R. Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
# author_summary: |
#   Lorem ipsum dolor sit amet, consectetur adipiscing elit.
header-includes: >
  \usepackage{indentfirst}
bibliography: ssc_bibliography.bib
output: 
  rticles::peerj_article:
    citation_package: natbib
    base_format: bookdown::pdf_document2 # for using \@ref()
---

@@

## Microsatellite genotyping Analysis {-}

@@

## Data analysis {-}

Isolates that fell into the 10 most abundant MCGs were subjected to an analysis of variance (ANOVA) in JMP version 12 to determine if their virulence levels were significantly different.
The mean separation was carried out using Tukey's HSD test.
Five microsatellite loci included compound repeats, where genotypes could not be unequivocally assigned based on the known repeat motifs and were consequently removed, resulting in 11 polymorphic loci selected for analysis (Table 2).
Since it could not be ruled out that isolates possessing the same genotype within the same field, year, and host were duplicate collections from the same plant, the data were first clone-corrected to remove these genotypes.
The data set was hierarchically reformatted to group isolates within each location/host/region/year and clones were removed at that level.
The clone-corrected data set included 318 isolates.
All analyses were performed on this data set unless otherwise mentioned.

## Distance-based redundancy analysis  {-}

A distance-based redundancy analysis (dbRDA) [@legendre1999distance] was performed with the function `capscale()` in the *vegan* 2.4-3 package in R (https://CRAN.R-project.org/package=vegan) to delineate relative contribution of phenotypic, spatial, and temporal components in influencing genetic composition of the populations. dbRDA is a method of conducting constrained ordinations on data matrices consisting of non-Euclidean distance measures.
RDA is a multivariate linear regression analysis of independent (explanatory: eg. environmental and phenotypic) variables on dependent (non-explanatory or response) variables.
In our case, a pairwise Bruvo's [@bruvo2004simple] distance matrix was generated from microsatellite data using *poppr* 2.4.1 [@kamvar2014poppr; @kamvar2015novel] and employed it as the dependent matrix for RDA analysis.
To identify environmental variable(s) correlated with genetic variation, a forward-backward selection process was applied with the vegan function `ordistep()` to identify the set of variables that explained more variation than predicted with the global model containing all variables.
An ANOVA was then performed to test for significance of the reduced model and marginal effects using 999 permutations.
The `varpart()` function of vegan was used to determine variation partitioning of explanatory variables.

## Shared Multilocus Genotype Community Analysis {-}

@@

## Discriminant analysis of principal components {-}

@@

## Molecular population statistics and linkage disequilibrium {-}

@@

## Results {-}

@@

@@

## dbRDA {-}

>>>>

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amadarasa
    email: bamadarasa2@unl.edu
    affiliation: 1
  - name: R. Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
header-includes: >
  \usepackage{indentfirst}
bibliography: ssc_bibliography.bib
output: 
  rticles::peerj_article:
    citation_package: natbib
    base_format: bookdown::pdf_document2 # for using \@ref()
---

@@

## Microsatellite genotyping {-}

@@

## Data processing and Analyses {-}

All data processing and analyses were performed in R version 3.4.0 [@R].
Of the 16 microsatellite loci, five included compound repeats, making allele scoring difficult. 
These loci were removed for the reported statistics, but were processed and included in data analyses to ensure the integrity of the results with 11 loci as compared to 16.
To control for non-independent samples (i.e. those sampled from the same location, region, year, and plant), data were clone-corrected for subsequent analyses.
The clone-corrected data set included 318 isolates.
All analyses were performed on this data set unless otherwise mentioned.
All data and analyses are openly available and reproducible at https://github.com/everhartlab/sclerotinia_366/

### Virulence Assessment {-}

We used analysis of variance (ANOVA) to assess if MCGs differed in severity.
We chose the top 10 MCGs, representing 57% of the isolates collected. Between-group differences were assessed using Tukey's HSD test using the `HSD.test()` function in the package *agricolae* version 1.2.4 [@mendiburu2015agricolae].

### Distance-based redundancy analysis  {-}

A distance-based redundancy analysis (dbRDA) [@legendre1999distance] was performed with the function `capscale()` in the *vegan* package version 2.4-3 [@vegan] to delineate relative contribution of phenotypic, spatial, and temporal components in influencing genetic composition of the populations. dbRDA is a method of conducting constrained ordinations on data matrices consisting of non-Euclidean distance measures.
RDA is a multivariate linear regression analysis of independent (explanatory: eg. environmental and phenotypic) variables on dependent (non-explanatory or response) variables.
In our case, a pairwise Bruvo's [@bruvo2004simple] distance matrix was generated from microsatellite data using *poppr* 2.4.1 [@kamvar2014poppr; @kamvar2015novel] and employed it as the dependent matrix for RDA analysis.
To identify environmental variable(s) correlated with genetic variation, a forward-backward selection process was applied with the vegan function `ordistep()` to identify the set of variables that explained more variation than predicted with the global model containing all variables.
An ANOVA was then performed to test for significance of the reduced model and marginal effects using 999 permutations.
The `varpart()` function of vegan was used to determine variation partitioning of explanatory variables.

### Shared Multilocus Genotype Community Analysis {-}

@@

### Discriminant analysis of principal components {-}

@@

### Molecular population statistics and linkage disequilibrium {-}

@@

# Results {-}

## Genotypic Structure {-}

@@

## Virulence {-}

@@

## Variable Importance {-}
